---
title: "Pie Chart"
author: "Adil Rasheed"
date: "2024-03-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Pie Chart for Categorical Data

```{r}
carb.count <- table(mtcars$carb)
carb.count
```
### Simple Pie Chart with Defult Arguments Values

```{r}
pie(carb.count)
```

### Show the pie chart on Clockwise

```{r}
# Show the pie chart on Clockwise
pie(carb.count, clockwise = T)
```

### Simple Pie Chart with Labels

```{r}
pie (carb.count, labels = carb.count)
```

### Pie Chat with Custimized lables names

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"))
```

### Pie Chat with Custimized lables names and increase the label size

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"), 
     cex = 2) # CEX increase the size of labels
```

### Pie Chat and adding customized colors

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"), 
     col = c("red", "blue", "green", "yellow", "black","grey"))
```

### Pie Chat and style of all border

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"), 
     col = c("red", "blue", "green", "yellow", "black","grey"),
             lty = 2)
```

### Pie Chat and add the density

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"), 
     col = c("red", "blue", "green", "yellow", "black","grey"),
             lty = 2,
             density= 50)
```

### Pie Chat with different angle

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"), 
     col = c("red", "blue", "green", "yellow", "black","grey"),
             lty = 2,
             density= 50,
     angle =90)
```

### Pie Chat and style the edges

```{r}
pie (carb.count, labels = c("one", "two", "three", "four", "five", "six"), 
     col = c("red", "blue", "green", "yellow", "black","grey"),
             lty = 2,
             density= 50,
     angle =90,
     edges = 10)
```

### Pie Chart with Legends

```{r}
pie (carb.count, labels = c("A", "B", "C", "D", "E", "F"), 
     col = rainbow (6)
     )
legend("topright", legend = c("A", "B", "C", "D", "E", "F"),
       fill = rainbow(6), title = "Legend"
       )
```

### 3D Pie Chart

```{r}
### pdf(filename.pdf)
## devoff()
pie3D(carb.count,
    col = rainbow(6),
    height = 0.2, # Height of the Pie Chart
    labelcol = "red",
    border = "black",
    explode = 0.25, # Used for create looks cake shape
    radius = 1.5, # used to expand the pie chart
    )
```
